Energy and the CES production function

### 2015-11-11 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now running off-axis models only when needed.

<<Other_Models, eval=FALSE>>=
# These models were estimated and the results sent to Paul Brockway.
# At this point, there is no reason to estimate the modesl every time.

# PT, unadjusted kl, quality-adjusted e
mod_PT_uakl_qae <- cesModel(iGDP ~ iKstkS.L + iL + iUMP + iYear, HistoricalData$PT, nest=c(1,2,3))
# PT, quality-adjusted kl, unadjusted e
mod_PT_qakl_uae <- cesModel(iGDP ~ iKservS.L + ihLest + iXpMP + iYear, HistoricalData$PT, nest=c(1,2,3))

# UK, unadjusted kl, quality-adjusted e
mod_UK_uakl_qae <- cesModel(iGDP ~ iKstkO.WwithRD + iL + iU + iYear, HistoricalData$UK, nest=c(1,2,3))
# UK, quality-adjusted kl, unadjusted e
mod_UK_qakl_uae <- cesModel(iGDP ~ iKservO.WwithRD + ihLest + iXp + iYear, HistoricalData$UK, nest=c(1,2,3))
@

>>>>

<<Other_Models, eval=FALSE>>=
# These models were estimated and the results sent to Paul Brockway.
# At this point, there is no reason to estimate the models every time.

fileNameOtherModels <- "EcolEcon2015kleOtherModelsCES.rds"

if (!rerunCESModels){
  # Load other models from the file on disk
  other_models <- readRDS(fileNameOtherModels)
} else {
  other_models <- list()
  # PT, unadjusted kl, quality-adjusted e
  other_models$PT$uakl_qae <- cesModel(iGDP ~ iKstkS.L + iL + iUMP + iYear, HistoricalData$PT, nest=c(1,2,3))
  # PT, quality-adjusted kl, unadjusted e
  other_models$PT$qakl_uae <- cesModel(iGDP ~ iKservS.L + ihLest + iXpMP + iYear, HistoricalData$PT, nest=c(1,2,3))
  # UK, unadjusted kl, quality-adjusted e
  other_models$UK$uakl_qae <- cesModel(iGDP ~ iKstkO.WwithRD + iL + iU + iYear, HistoricalData$UK, nest=c(1,2,3))
  # UK, quality-adjusted kl, unadjusted e
  other_models$UK$qakl_uae <- cesModel(iGDP ~ iKservO.WwithRD + ihLest + iXp + iYear, HistoricalData$UK, nest=c(1,2,3))
  saveRDS(other_models, fileNameOtherModels)
}
